### 2011-05-05 paper/paper.tex
blah
section 5.3

\begin{theorem}[{\bf Hit-and-run bound}] Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$m = \displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the total variation distance of the chain is within $\epsilon$ of the uniform distribution. That is, if $\mu$ is the uniform distribution and $\sigma$ is the the distribution of the chain after $m$ steps, then
\begin{center}$\displaystyle \sup_{r \in \mathcal{R}} |\mu(r) - \sigma(r)| \le \epsilon$.\end{center}
\end{theorem}

@@

>>>>

\begin{theorem}[{\bf Hit-and-run bound}] Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$m = \displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the total variation distance of the chain is within $\epsilon$ of the uniform distribution. That is, if $\mu$ is the uniform distribution and $P$ is the the distribution of the chain after $m$ steps, then
\begin{center}$\displaystyle \sup_{r \in \mathcal{R}} |\mu(r) - P(r)| \le \epsilon$.\end{center}
\end{theorem}

@@

\subsection{The sampling}

For each sampling method and for each test case, we generated $1000$ samples. In most cases, we used $5000$ iterations of our random walk's transition function in order to generate each sample. However, as noted above, the hit-and-run method is slower due to its binary search. We binary search up to a precision of $10^{-12}$, which requires approximately $40$ calls to the membership oracle for each endpoint. We found empirically that transitioning only $1200$ times caused it to run just about as fast as the other methods on $5000$ transitions. Therefore, we also ran tests with only $1200$ transitions for the hit-and-run.
